The problem and promise of scale in animal social multilayer networks

### 2020-08-27 paper/manuscript.Rmd
digits
reorder a, b, c nobs

options(digits = 2, round = 2)

@@

As the number of observations used to generate multilayer networks increased,
individuals became more connected and variance in metrics decreased. Edge
overlap increased across all three habitat layers with increasing number of
observations (Figure \@ref(fig:nobs) B). Similarly, multidegree for all
individuals increased quickly between 10 and 100 observations and continued to
increase until 1000 observations (Figure \@ref(fig:nobs) C). Graph strength
across individuals in all three habitat layers was highly variable at low number
of observations and variance decreased after ~100 observations (Figure
\@ref(fig:nobs) A). Since the variance in these multilayer metrics decreases
after a certain number of observations, this sensitivity method could be useful
for determining the number of observations necessary for sufficiently describing
social dynamics across contexts.

>>>>

options(digits = 1, round = 2)

@@

As the number of observations used to generate multilayer networks increased,
individuals became more connected and variance in metrics decreased. Graph
strength across individuals in all three habitat layers was highly variable at
low number of observations and variance decreased after ~100 observations
(Figure \@ref(fig:nobs) A). Edge overlap increased across all three habitat
layers with increasing number of observations (Figure \@ref(fig:nobs) B).
Similarly, multidegree for all individuals increased quickly between 10 and 100
observations and continued to increase until 1000 observations (Figure
\@ref(fig:nobs) C).  Since the variance in these multilayer metrics decreases
after a certain number of observations, this sensitivity method could be useful
for determining the number of observations necessary for sufficiently describing
social dynamics across contexts.
